Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-10-09 pirouette_supplement.tex
Transferred richelbilderbeek/mcbette to ropensci/mcbette

Until it is on CRAN, and for the most up-to-date version, 
one can download and install the package from \verb;pirouette;'s GitHub 
repository. We first need the \verb;mcbette; and \verb;nodeSub; packages:
\begin{lstlisting}[
    language = R,
    floatplacement = ht,
    frame = single
]
remotes::install_github(
  "richelbilderbeek/mcbette"
)
remotes::install_github(
  "thijsjanzen/nodeSub"
)
\end{lstlisting}

>>>>

Until it is on CRAN, and for the most up-to-date version, 
one can download and install the package from \verb;pirouette;'s GitHub 
repository. We first need the \verb;mcbette; and \verb;nodeSub; packages:
\begin{lstlisting}[
    language = R,
    floatplacement = ht,
    frame = single
]
remotes::install_github(
  "ropensci/mcbette"
)
remotes::install_github(
  "thijsjanzen/nodeSub"
)
\end{lstlisting}
